### 2020-05-31 README.Rmd
Add graph to readme

For most users, the recommended starting point is to read [the preprint paper, available on the Open Science Framework](https://osf.io/zcvbs/).

The paper describes the WORCS workflow, and how the `worcs` package fits into that workflow.

>>>>

For most users, the recommended starting point is to [read the preprint paper](https://osf.io/zcvbs/),
which introduces the WORCS workflow, explains the underlying tools, and illustrates how the `worcs` package can be used to create a new project that follows the workflow.

The workflow is illustrated below; the [workflow vignette](https://cjvanlissa.github.io/worcs/articles/workflow.html) describes each step in detail.

```{r, echo = FALSE}
knitr::include_graphics("paper/workflow_graph/workflow.png")
```
